Structured Versus Decorated Cospans

### 2020-11-20 cospans.tex
changed \mathbb{H} to \H (again!)

%a morphism from $F\lCsp$ to $F' \lCsp$ will then be a double functor $\mathbb{H} \maps F\lCsp \to F' \lCsp$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \maps \A \to \mathsf{A'}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:

@@

and then the image of this 2-morphism under the double functor $\mathbb{H}$ is given by:

@@

On the other hand, applying the double functor $\mathbb{H}$ first gives:

@@

This double functor $\mathbb{H}$ satisfies the equations $S \mathbb{H}_1 = HS$ and $T \mathbb{H}_1=HT$.

@@

where $$d \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\mathbb{H}(M \odot N)$:

@@

\node (D) at (2,-0.5) {$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F'(H(c_1 +_b c_2))$};

@@

where $$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F'(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\mathbb{H}$ is given respectively by $\mathbb{H}(M)$ and $\mathbb{H}(N)$:

@@

Composing these then gives $\mathbb{H}(M) \odot \mathbb{H}(N)$:

@@

\node (D) at (2.25,-0.5) {$d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \in F'(H(c_1) +_{H(b)} H(c_2))$};

@@

where $$\hspace{-.4in}\scriptstyle{d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \maps 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F'(H(c_1)+ H(c_2)) \xrightarrow{F' (J)} F'(H(c_1) +_{H(b)} H(c_2)).}$$
We then have a comparison constraint: $$\mathbb{H}_{M,N} \maps \mathbb{H}(M) \odot \mathbb{H}(N) \xrightarrow{\sim} \mathbb{H}(M \odot N)$$given by the globular 2-isomorphism:

@@

\node (E) at (7.5,0.5) {$d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \in F'(H(c_1)+_{H(b_1)}H(c_2))$};
\node (F) at (7.5,-0.5) {$d_{\mathbb{H}(M \odot N)} \in F'(H(c_1 +_b c_2))$};
\node (G) at (2.5,-1) {$\tau_{\kappa^{-1}} \maps F'(\kappa^{-1})(d_{\mathbb{H}(M) \odot \mathbb{H}(N)}) \to d_{\mathbb{H}(M \odot N)}.$};

@@

where $\kappa$ is the isomorphism $$\kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$. The above diagram commutes by a similar argument to the one used in \cref{thm:equiv}. Similarly, for every object $c \in \A$, we have a unit comparison constraint $$\mathbb{H}_U \maps U_{\mathbb{H}(c)} \to \mathbb{H}(U_c)$$ given by the globular 2-isomorphism:

@@

\node (A) at (0,0.5) {$(\mathbb{H}(M) \odot \mathbb{H}(N)) \odot \mathbb{H}(P)$};
\node (B) at (0,-0.5) {$\mathbb{H}(M \odot N) \odot \mathbb{H}(P)$};
\node (C) at (0,-1.5) {$\mathbb{H}((M \odot N) \odot P)$};
\node (A') at (3,0.5) {$\mathbb{H}(M) \odot (\mathbb{H}(N) \odot \mathbb{H}(P))$};
\node (B') at (3,-0.5) {$\mathbb{H}(M) \odot \mathbb{H}(N \odot P)$};
\node (C') at (3,-1.5) {$\mathbb{H}(M \odot (N \odot P))$};
(A) edge node[left]{$\mathbb{H}_{M,N} \odot 1$} (B)
(B) edge node[left]{$\mathbb{H}_{M \odot N,P}$} (C)

@@

(C) edge node [above] {$\mathbb{H}(a')$} (C')
(B') edge node [right] {$\mathbb{H}_{M,N \odot P}$} (C')
(A') edge node [right]{$1 \odot \mathbb{H}_{N,P}$} (B');

@@

\node (A) at (0,0) {$U_{\mathbb{H}(a)} \odot \mathbb{H}(M)$};
\node (B) at (2.5,0) {$\mathbb{H}(U_a) \odot \mathbb{H}(M)$};
\node (C) at (0,-1) {$\mathbb{H}(M)$};
\node (D) at (2.5,-1) {$\mathbb{H}(U_a \odot M)$};
\node (A') at (5,0) {$\mathbb{H}(M) \odot U_{\mathbb{H}(b)}$};
\node (B') at (7.5,0) {$\mathbb{H}(M) \odot \mathbb{H}(U_b)$};
\node (C') at (5,-1) {$\mathbb{H}(M)$};
\node (D') at (7.5,-1) {$\mathbb{H}(M \odot U_b)$};

@@

(A) edge node[above]{$\mathbb{H}_U \odot 1$} (B)

@@

(B) edge node[right]{$\mathbb{H}_{U_a,M}$} (D)
(D) edge node[above]{$\mathbb{H}(\lambda')$} (C)
(A') edge node[above]{$1 \odot \mathbb{H}_U$} (B')

@@

(B') edge node[right]{$\mathbb{H}_{M,U_b}$} (D')
(D') edge node[above]{$\mathbb{H}(\rho')$} (C');

@@

The diagrams involving the morphisms of decorations are similar to those in Theorem \cref{DC}. This shows that $\mathbb{H}=(H,E,\theta)$ is a double functor. Next we show that this double functor is symmetric monoidal. First, that the object component $\mathbb{H}_0=H$ is symmetric monoidal is clear as $H \maps \A \to \A'$ preserves finite colimits. As for the arrow component $\mathbb{H}_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\lCsp$:

@@

and the image of this horizontal 1-cell under the double functor $\mathbb{H}$ is $\mathbb{H}(M_1 \otimes M_2)$ given by:

@@

\node (D) at (2,-0.5) {$d_{\mathbb{H}(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F'(H(c_1+c_2))$};

@@

On the other hand, the image of $M_1$ and $M_2$ is given by $\mathbb{H}(M_1)$ and $\mathbb{H}(M_2)$:

@@

\node (D) at (1.5,-0.5) {$d_{\mathbb{H}(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F'(H(c_1))$};

@@

\node (H) at (6,-0.5) {$d_{\mathbb{H}(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F'(H(c_2))$};

@@

and their tensor product $\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)$ is given by:

@@

\node (D) at (2.5,-0.5) {$d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \in F'(H(c_1)+H(c_2))$};

@@

$$\hspace{-.4in} \scriptstyle{d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F' (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \mathbb{H}(M_1) \otimes \mathbb{H}(M_2) \to \mathbb{H}(M_1 \otimes M_2)$ in $F'\lCsp$ given by:

@@

\node (E) at (2.5,1) {$d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \in F'(H(c_1)+H(c_2))$};
\node (F) at (2.5,-1) {$d_{\mathbb{H}(M_1 \otimes M_2)} \in F'(H(c_1+c_2))$};

@@

$$\tau_\kappa \maps F'(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)}) \to d_{\mathbb{H}(M_1 \otimes M_2)}$$

@@

\node (A) at (0,0.5) {$(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)$};
\node (B) at (0,-0.5) {$\mathbb{H}(M_1 \otimes M_2) \otimes \mathbb{H}(M_3)$};
\node (C) at (0,-1.5) {$\mathbb{H}((M_1 \otimes M_2) \otimes M_3)$};
\node (A') at (4,0.5) {$\mathbb{H}(M_1) \otimes (\mathbb{H}(M_2) \otimes \mathbb{H}(M_3))$};
\node (B') at (4,-0.5) {$\mathbb{H}(M_1) \otimes \mathbb{H}(M_2 \otimes M_3)$};
\node (C') at (4,-1.5) {$\mathbb{H}(M_1 \otimes (M_2 \otimes M_3))$};

@@

(C) edge node [above] {$\mathbb{H}(\alpha)$} (C')

@@

\node (A) at (0,0.5) {$F'(\alpha \kappa \kappa)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)})$};
\node (B) at (0,-0.5) {$F'(\alpha \kappa)(d_{\mathbb{H}(M_1 \otimes M_2) \otimes \mathbb{H}(M_3)})$};
\node (C) at (0,-1.5) {$F'(\alpha)(d_{\mathbb{H}((M_1 \otimes M_2) \otimes M_3)})$};
\node (A') at (5,0.5) {$F'(\kappa \kappa)(d_{\mathbb{H}(M_1) \otimes (\mathbb{H}(M_2) \otimes \mathbb{H}(M_3))})$};
\node (B') at (5,-0.5) {$F'(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2 \otimes M_3)})$};
\node (C') at (5,-1.5) {$d_{\mathbb{H}(M_1 \otimes (M_2 \otimes M_3))}$};

@@

where $$F'(\alpha \kappa \kappa)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)}) = F'(\kappa \kappa \alpha')(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)})$$

@@

where $1_\A$ is the monoidal unit of the cocartesian category $\A$. The image of this horizontal 1-cell under $\mathbb{H}$ is given by:

@@

as $H$ preserves finite colimits. We then have a 2-isomorphism in $F'\lCsp$ given by: $$\mu \maps 1_{F'\lCsp_1} \to \mathbb{H}(1_{F\lCsp_1})$$ 

@@

\node (A) at (0,0) {$1_\mathsf{A'} \otimes \mathbb{H}(M)$};
\node (B) at (2.5,0) {$\mathbb{H}(1_\A) \otimes \mathbb{H}(M)$};
\node (C) at (0,-1) {$\mathbb{H}(M)$};
\node (D) at (2.5,-1) {$\mathbb{H}(1_\A \otimes M)$};

@@

(D) edge node[above]{$\mathbb{H}(\ell')$} (C);

@@

\node (A) at (0,0.5) {$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})$};
\node (B) at (0,-0.5) {$d_{\mathbb{H}(M)}$};
\node (A') at (4,0.5) {$F'(H(\ell') \kappa)(d_{!_{\mathbb{H}(1_\A)}}\otimes d_{\mathbb{H}(M)})$};
\node (B') at (4,-0.5) {$F'(H(\ell'))(d_{\mathbb{H}(1_\A \otimes M)})$};

@@

where $$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})=F'(H(\ell')\kappa(\mu \otimes 1))(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes. The other square involving the right unitors $r$ and $r'$ is similar. Note that because the comparison constraints $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\mathbb{H}$ is strong.

@@

We thus have two symmetric monoidal double categories: ${}_L \lCsp(\Graph)$ obtained from structured cospans and $F\lCsp$ obtained from decorated cospans. Both of these double categories have $\Set$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms.  One can show using Theorem \cref{thm:equiv} that $_L \lCsp(\Graph)$ and $F\lCsp$ are equivalent as symmetric monoidal double categories.

>>>>

%a morphism from $F\lCsp$ to $F' \lCsp$ will then be a double functor $\H \maps F\lCsp \to F' \lCsp$ whose object component is given by a finite colimit preserving functor $\H_0 = H \maps \A \to \mathsf{A'}$ and whose arrow component is given by a functor $\H_1$ defined on horizontal 1-cells by:

@@

and then the image of this 2-morphism under the double functor $\H$ is given by:

@@

On the other hand, applying the double functor $\H$ first gives:

@@

This double functor $\H$ satisfies the equations $S \H_1 = HS$ and $T \H_1=HT$.

@@

where $$d \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\H(M \odot N)$:

@@

\node (D) at (2,-0.5) {$\H(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F'(H(c_1 +_b c_2))$};

@@

where $$\H(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F'(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\H$ is given respectively by $\H(M)$ and $\H(N)$:

@@

Composing these then gives $\H(M) \odot \H(N)$:

@@

\node (D) at (2.25,-0.5) {$d_{\H(M) \odot \H(N)} \in F'(H(c_1) +_{H(b)} H(c_2))$};

@@

where $$\hspace{-.4in}\scriptstyle{d_{\H(M) \odot \H(N)} \maps 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F'(H(c_1)+ H(c_2)) \xrightarrow{F' (J)} F'(H(c_1) +_{H(b)} H(c_2)).}$$
We then have a comparison constraint: $$\H_{M,N} \maps \H(M) \odot \H(N) \xrightarrow{\sim} \H(M \odot N)$$given by the globular 2-isomorphism:

@@

\node (E) at (7.5,0.5) {$d_{\H(M) \odot \H(N)} \in F'(H(c_1)+_{H(b_1)}H(c_2))$};
\node (F) at (7.5,-0.5) {$d_{\H(M \odot N)} \in F'(H(c_1 +_b c_2))$};
\node (G) at (2.5,-1) {$\tau_{\kappa^{-1}} \maps F'(\kappa^{-1})(d_{\H(M) \odot \H(N)}) \to d_{\H(M \odot N)}.$};

@@

where $\kappa$ is the isomorphism $$\kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$. The above diagram commutes by a similar argument to the one used in \cref{thm:equiv}. Similarly, for every object $c \in \A$, we have a unit comparison constraint $$\H_U \maps U_{\H(c)} \to \H(U_c)$$ given by the globular 2-isomorphism:

@@

\node (A) at (0,0.5) {$(\H(M) \odot \H(N)) \odot \H(P)$};
\node (B) at (0,-0.5) {$\H(M \odot N) \odot \H(P)$};
\node (C) at (0,-1.5) {$\H((M \odot N) \odot P)$};
\node (A') at (3,0.5) {$\H(M) \odot (\H(N) \odot \H(P))$};
\node (B') at (3,-0.5) {$\H(M) \odot \H(N \odot P)$};
\node (C') at (3,-1.5) {$\H(M \odot (N \odot P))$};
(A) edge node[left]{$\H_{M,N} \odot 1$} (B)
(B) edge node[left]{$\H_{M \odot N,P}$} (C)

@@

(C) edge node [above] {$\H(a')$} (C')
(B') edge node [right] {$\H_{M,N \odot P}$} (C')
(A') edge node [right]{$1 \odot \H_{N,P}$} (B');

@@

\node (A) at (0,0) {$U_{\H(a)} \odot \H(M)$};
\node (B) at (2.5,0) {$\H(U_a) \odot \H(M)$};
\node (C) at (0,-1) {$\H(M)$};
\node (D) at (2.5,-1) {$\H(U_a \odot M)$};
\node (A') at (5,0) {$\H(M) \odot U_{\H(b)}$};
\node (B') at (7.5,0) {$\H(M) \odot \H(U_b)$};
\node (C') at (5,-1) {$\H(M)$};
\node (D') at (7.5,-1) {$\H(M \odot U_b)$};

@@

(A) edge node[above]{$\H_U \odot 1$} (B)

@@

(B) edge node[right]{$\H_{U_a,M}$} (D)
(D) edge node[above]{$\H(\lambda')$} (C)
(A') edge node[above]{$1 \odot \H_U$} (B')

@@

(B') edge node[right]{$\H_{M,U_b}$} (D')
(D') edge node[above]{$\H(\rho')$} (C');

@@

The diagrams involving the morphisms of decorations are similar to those in Theorem \cref{DC}. This shows that $\H=(H,E,\theta)$ is a double functor. Next we show that this double functor is symmetric monoidal. First, that the object component $\H_0=H$ is symmetric monoidal is clear as $H \maps \A \to \A'$ preserves finite colimits. As for the arrow component $\H_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\lCsp$:

@@

and the image of this horizontal 1-cell under the double functor $\H$ is $\H(M_1 \otimes M_2)$ given by:

@@

\node (D) at (2,-0.5) {$d_{\H(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F'(H(c_1+c_2))$};

@@

On the other hand, the image of $M_1$ and $M_2$ is given by $\H(M_1)$ and $\H(M_2)$:

@@

\node (D) at (1.5,-0.5) {$d_{\H(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F'(H(c_1))$};

@@

\node (H) at (6,-0.5) {$d_{\H(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F'(H(c_2))$};

@@

and their tensor product $\H(M_1) \otimes \H(M_2)$ is given by:

@@

\node (D) at (2.5,-0.5) {$d_{\H(M_1) \otimes \H(M_2)} \in F'(H(c_1)+H(c_2))$};

@@

$$\hspace{-.4in} \scriptstyle{d_{\H(M_1) \otimes \H(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F' (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \H(M_1) \otimes \H(M_2) \to \H(M_1 \otimes M_2)$ in $F'\lCsp$ given by:

@@

\node (E) at (2.5,1) {$d_{\H(M_1) \otimes \H(M_2)} \in F'(H(c_1)+H(c_2))$};
\node (F) at (2.5,-1) {$d_{\H(M_1 \otimes M_2)} \in F'(H(c_1+c_2))$};

@@

$$\tau_\kappa \maps F'(\kappa)(d_{\H(M_1) \otimes \H(M_2)}) \to d_{\H(M_1 \otimes M_2)}$$

@@

\node (A) at (0,0.5) {$(\H(M_1) \otimes \H(M_2)) \otimes \H(M_3)$};
\node (B) at (0,-0.5) {$\H(M_1 \otimes M_2) \otimes \H(M_3)$};
\node (C) at (0,-1.5) {$\H((M_1 \otimes M_2) \otimes M_3)$};
\node (A') at (4,0.5) {$\H(M_1) \otimes (\H(M_2) \otimes \H(M_3))$};
\node (B') at (4,-0.5) {$\H(M_1) \otimes \H(M_2 \otimes M_3)$};
\node (C') at (4,-1.5) {$\H(M_1 \otimes (M_2 \otimes M_3))$};

@@

(C) edge node [above] {$\H(\alpha)$} (C')

@@

\node (A) at (0,0.5) {$F'(\alpha \kappa \kappa)(d_{(\H(M_1) \otimes \H(M_2)) \otimes \H(M_3)})$};
\node (B) at (0,-0.5) {$F'(\alpha \kappa)(d_{\H(M_1 \otimes M_2) \otimes \H(M_3)})$};
\node (C) at (0,-1.5) {$F'(\alpha)(d_{\H((M_1 \otimes M_2) \otimes M_3)})$};
\node (A') at (5,0.5) {$F'(\kappa \kappa)(d_{\H(M_1) \otimes (\H(M_2) \otimes \H(M_3))})$};
\node (B') at (5,-0.5) {$F'(\kappa)(d_{\H(M_1) \otimes \H(M_2 \otimes M_3)})$};
\node (C') at (5,-1.5) {$d_{\H(M_1 \otimes (M_2 \otimes M_3))}$};

@@

where $$F'(\alpha \kappa \kappa)(d_{(\H(M_1) \otimes \H(M_2)) \otimes \H(M_3)}) = F'(\kappa \kappa \alpha')(d_{(\H(M_1) \otimes \H(M_2)) \otimes \H(M_3)})$$

@@

where $1_\A$ is the monoidal unit of the cocartesian category $\A$. The image of this horizontal 1-cell under $\H$ is given by:

@@

as $H$ preserves finite colimits. We then have a 2-isomorphism in $F'\lCsp$ given by: $$\mu \maps 1_{F'\lCsp_1} \to \H(1_{F\lCsp_1})$$ 

@@

\node (A) at (0,0) {$1_\mathsf{A'} \otimes \H(M)$};
\node (B) at (2.5,0) {$\H(1_\A) \otimes \H(M)$};
\node (C) at (0,-1) {$\H(M)$};
\node (D) at (2.5,-1) {$\H(1_\A \otimes M)$};

@@

(D) edge node[above]{$\H(\ell')$} (C);

@@

\node (A) at (0,0.5) {$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\H(M)})$};
\node (B) at (0,-0.5) {$d_{\H(M)}$};
\node (A') at (4,0.5) {$F'(H(\ell') \kappa)(d_{!_{\H(1_\A)}}\otimes d_{\H(M)})$};
\node (B') at (4,-0.5) {$F'(H(\ell'))(d_{\H(1_\A \otimes M)})$};

@@

where $$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\H(M)})=F'(H(\ell')\kappa(\mu \otimes 1))(d_{!_{1_\mathsf{A'}}} \otimes d_{\H(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes. The other square involving the right unitors $r$ and $r'$ is similar. Note that because the comparison constraints $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\H$ is strong.

@@

We thus have two symmetric monoidal double categories: ${}_L \lCsp(\Graph)$ obtained from structured cospans and $F\lCsp$ obtained from decorated cospans. Both of these double categories have $\Set$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms.  One can show using \cref{thm:equiv} that $_L \lCsp(\Graph)$ and $F\lCsp$ are equivalent as symmetric monoidal double categories.
